Finite element analysis of multi-dimensional and simplified models for beams

### 2024-04-18 final_seminar/main.tex
presentaion

\section{Validity of the Timoshenko beam model}
    \begin{frame}{Validity of the Timoshenko beam model}
        \begin{center}
            \begin{minipage}[b]{0.45\linewidth}
                \centering
                \begin{tikzpicture}[scale=0.7]
                    \draw[line width = 0.4mm] (0,0.2) -- (6,0.2);
                                \draw[line width = 0.4mm] (0,-0.2) -- (6,-0.2);
                                \draw[line width = 0.4mm] (6,-0.2) -- (6,0.2);

@@

                            \draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
                            \draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
                            \draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
                            \draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
                            \draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
                            \draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
                            \draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
                            \draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
                \end{tikzpicture}
                \captionof{figure}{Timoshenko Beam}
            \end{minipage}
        \end{center}
    \end{frame}

    \begin{frame}{Comparison of two and three-dimensional models}
        \centering
        \begin{minipage}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{Beam1.jpg}
            \\ 2D Beam Type - $\lambda_6 = 21.911$
            \label{fig:minipage2}
        \end{minipage}
        \hfill
        \begin{minipage}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{1DBeam2.png}
            \\ Timoshenko - $\lambda_5 = 21.794$
            \label{fig:minipage1}
        \end{minipage}
        \vspace{1em}
        \begin{minipage}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{Beam2.jpg}
            \\ 2D Beam Type - $\lambda_7 = 45.711$
            \label{fig:minipage4}
        \end{minipage}
        \hfill
        \begin{minipage}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{1DBeam1.png}
            \\ Timoshenko - $\lambda_6 = 45.390$
            \label{fig:minipage3}
        \end{minipage}
        \\ Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).
    \end{frame}

    \begin{frame}{Comparison of two and three-dimensional models}
        \centering
        \begin{minipage}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{NotBeam1.jpg}
            \\ Non-Beam Type - $\lambda_4 = 7.7077$
            \label{fig:nonbeam1}
        \end{minipage}
        \hfill
        \begin{minipage}[b]{0.45\textwidth}
            \includegraphics[width=\textwidth]{NotBeam2.jpg}
            \\ Non-Beam Type - $\lambda_8 = 69.344$
            \label{fig:nonbeam2}
        \end{minipage}
        \\ Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.
    \end{frame}

    \begin{frame}{Comparison of two and three-dimensional models}
        \centering
        \footnotesize
        \renewcommand{\arraystretch}{0.9}
        Results from \cite{LVV09} and results obtained. $0^a$ indicates a 0 due to rounding. Height to lenght ratio of 1 to 10.

@@

    \begin{frame}{Comparison of Eigenvalues across Different Parameters}
        \centering
        \footnotesize
        \renewcommand{\arraystretch}{0.8}
        \resizebox{\textwidth}{!}{%
        \begin{tabular}{|cccc||cccc||cccc||cccc|}
            \hline
            \multicolumn{16}{|c|}{Comparison of Eigenvalues} \\
            \hline\hline
            \multicolumn{4}{|c||}{ $h = 1/5$ or $\alpha = 300$} & \multicolumn{4}{c||}{$h =1/10$ or $\alpha = 1200$} & \multicolumn{4}{c||}{$h = 1/20$ or $\alpha = 4800$} & \multicolumn{4}{c|}{$h = 1/30$ or $\alpha = 10800$} \\
            \hline

            {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} \\
            \hline
            {1}&0.12151&1&0.12092&1&0.031713&1&0.031639&1&0.008013&1&0.008004&1&0.003568&1&0.003565\\
            {2}&3.5460&2&3.5071&2&1.1413&2     & 1.1365 & 2     & 0.30756 & 2     & 0.30705 & 2     & 0.13869 & 2     & 0.13855 \\
            {3} & {7.7311} &       & {-} & {3}     & {7.7161} &       & {-} & 3     & 2.3273 & 3     & 2.3213 & 3     & 1.0698 & 3     & 1.0683 \\
            {4} & 20.225 & 3     & 19.869 & 4     & 7.9180 & 3     & 7.8617 & {4}     & {7.7077} &       & {-} & 4     & 4.0140 & 4     & 4.0058 \\
            {5} & 56.109 & 4     & 54.766 & 5     & 26.148 & 4     & 25.869 & 5     & 8.5086 & 4     & 8.4762 & {5}     & {7.7047} &       & {-} \\
            {6} & {69.164} &       & {-} & 6     & 60.816 & 5     & 59.946 & 6     & 21.911 & 5     & 21.794 & 6     & 10.655 & 5     & 10.625 \\
            {7} & 114.03 & 5     & 110.75 & {7}     & {69.344} &       & {-} & 7     & 45.711 & 6     & 45.390 & 7     & 22.975 & 6     & 22.890 \\
            {8} & {189.17} &  6     & {186.50} & 8     & 115.28 & 6     & 113.23 & {8}     & {69.344} &       & {-} & 8     & 43.113 & 7     & 42.909 \\
            {9} & {192.61} &      &  & {9}     & {191.57} &   7  & {187.55} & 9     & 82.887 & 7     & 82.154 & {9}     & {69.331} &       & {-} \\
            {10} & 285.85 & 7     & 277.64 & {10}    & {192.03} &      & {-} & 10    & 136.03 & 8     & 134.58 & 10    & 73.230 & 8     & 72.803 \\
            {11} & 328.40 & 8     & 330.29 & 11    & 290.76 & 8     & 283.81 & {11}    & {192.48} &       & {-} & 11    & 115.41 & 9     & 114.61 \\
            {12} & {357.08} &       & {-} & {12}    & {374.45} &       & {-} & 12    & 207.29 & 9     & 204.69 & 12    & 171.61 & 10    & 170.20 \\
            {13} & 397.33 & 9     & 394.02 & 13    & 413.20 & 9     & 402.27 & 13    & 298.38 & 10    & 294.10 & {13}    & {192.52} &       & {-} \\
            {14} & 442.00   & 10    & 439.52 & 14    & 558.67 & 10    & 542.65 & {14}    & {376.83} &       & {-} & 14    & 243.56 & 11    & 241.26 \\
            {15} & {533.71} &       & {-} & {15}    & {614.11} &       & {-} & 15    & 410.63 & 11    & 404.01 & 15    & 332.83 & 12    & 329.28 \\
            {16} & 538.97 & 11    & 541.55 & 16    & 726.26 & 11    & 704.15 & 16    & 545.03 & 12    & 535.32 & {16}    & {377.16} &       & {-} \\
            {17} & {596.06} &       & {-} & {17}    & {906.28} &       & {-} & {17}    & {621.95} &       & {-} & 17    & 440.77 & 13    & 435.51 \\
            {18} & 602.77 & 12    & 596.09 & 18    & 913.69 & 12    & 884.92 & 18    & 702.30 & 13    & 688.64 & 18    & 568.51 & 14    & 561.04 \\
            {19} & {657.87} &       & {-} & 19    & 1113.7 & 13    & 1080.1 & 19    & 882.95 & 14    & 864.40 & {19}    & {623.05} &       & {-} \\
            {20} & 717.37 & 13    & 731.74 & {20}    & {1218.0}  &       & {-} & {20}    & {927.18} &       & {-} & 20    & 717.04 & 15    & 706.74 \\
            \hline
            \multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.1718\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{3.1486\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.1018\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{1.4361\%} \\
            \hline
        \end{tabular}}
    \end{frame}

\section{Validity of the Two-dimensional beam model}
    \begin{frame}{Validity of the Two-dimensional beam model}
        \begin{center}
            \begin{minipage}[b]{0.45\linewidth}
                \centering
                \begin{tikzpicture}[scale=0.6]
                    \draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
                    \draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
                    \draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
                    \draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);

@@

    \begin{frame}
        \begin{table}[htbp]
            \scalebox{.8}{
            \makebox[\textwidth]{
                \begin{tabular}{|cc|cc|cc|cc||cc|}
                    \hline
                    \multicolumn{10}{|c|}{{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.} \\
                    \hline
                    \hline
                    i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
                    \hline
                    {2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
                    {3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
                    \rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
                    {8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
                    {10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
                    \rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
                    {14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
                    \rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
                    {18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
                    {21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
                    {23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
                    \rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
                    {27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
                    {30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
                    \rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
                    {34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
                    \rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
                    {39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
                    \rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
                    {44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
                    \hline
                    \hline
                    \multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
                    \hline
                \end{tabular}%
                \label{tab:2v3_1}%
            }}
        \end{table}%
    \end{frame}

@@

\section{Conclusion}
    \begin{frame}{Conclusion}
    \end{frame}

>>>>

    \subsection{Validity of the Timoshenko beam}
        \begin{frame}{Validity of the Timoshenko beam - Visual representation}
            \begin{center}
                \begin{minipage}[b]{0.45\linewidth}
                    \centering
                    \begin{tikzpicture}[scale=0.7]
                        \draw[line width = 0.4mm] (0,0.2) -- (6,0.2);
                                    \draw[line width = 0.4mm] (0,-0.2) -- (6,-0.2);
                                    \draw[line width = 0.4mm] (6,-0.2) -- (6,0.2);

@@

                                \draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
                                \draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
                                \draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
                                \draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
                                \draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
                                \draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
                                \draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
                                \draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
                    \end{tikzpicture}
                    \captionof{figure}{Timoshenko Beam}
                \end{minipage}
            \end{center}

            \only<2->{
                Parameters:

                For the Timoshenko beam model we do not have a direct parameter for the height.

                Recall the dimensionless constant $\alpha$ in the Timoshenko beam model. In the derivation of the dimensionless form, the following relation was obtained:

                \[ \alpha = \frac{A\ell^2}{I}\]

                Where $A$ is the area of the cross-section, $\ell$ is the length of the beam and $I$ is the area moment of inertia.
            }

            \only<3->{
                \[A = hb, \ I = \frac{h^3b}{12} \implies h = \sqrt{\frac{12}{\alpha}}\]
            }

        \begin{frame}{Validity of the Timoshenko beam - Beam type mode shapes}
            \centering
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{Beam1.jpg}
                \\ 2D Beam Type - $\lambda_6 = 21.911$
                \label{fig:minipage2}
            \end{minipage}
            \hfill
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{1DBeam2.png}
                \\ Timoshenko - $\lambda_5 = 21.794$
                \label{fig:minipage1}
            \end{minipage}
            \vspace{1em}
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{Beam2.jpg}
                \\ 2D Beam Type - $\lambda_7 = 45.711$
                \label{fig:minipage4}
            \end{minipage}
            \hfill
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{1DBeam1.png}
                \\ Timoshenko - $\lambda_6 = 45.390$
                \label{fig:minipage3}
            \end{minipage}
            \\ Modal shapes of the displacement $w$ for the beam-type 2D body and the Timoshenko beam with $\alpha = 4800$ ($h = 1/20$).
        \end{frame}

        \begin{frame}{Validity of the Timoshenko beam - Non-beam type mode shapes}
            \centering
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{NotBeam1.jpg}
                \\ Non-Beam Type - $\lambda_4 = 7.7077$
                \label{fig:nonbeam1}
            \end{minipage}
            \hfill
            \begin{minipage}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{NotBeam2.jpg}
                \\ Non-Beam Type - $\lambda_8 = 69.344$
                \label{fig:nonbeam2}
            \end{minipage}
            \\ Modal shapes of the displacement $w$ for the non-beam type 2D body with $h = 1/20$.
        \end{frame}

        \begin{frame}{Validity of the Timoshenko beam - Direct comparison of displacement mode shapes}
            \centering
            \includegraphics[scale=0.2]{1Dv2D.png} % Adjust scale as needed
            \par
            \footnotesize Comparison of the displacement $w$ mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)
        \end{frame}

        \begin{frame}{Validity of the Timoshenko beam - Direct comparison of rotation mode shapes}
            \centering
            \includegraphics[scale=0.2]{1Dv2Dphi.png} % Adjust scale as needed
            \par
            \footnotesize Comparison of the angle $\phi$ (best fit for 2D Beam) mode shape corresponding to $\lambda_{10}$ for the 2D beam and $\lambda_8$ for the Timoshenko beam with $\alpha = 4800$ ($h=1/20$)

            \begin{figure}[h!]
                \centering
                \begin{tikzpicture}[scale=0.4]

                \draw[line width = 0.4mm] (0,1) -- (7,1);
                \draw[line width = 0.4mm] (0,-1) -- (7,-1);
                \draw[line width = 0.4mm] (7,-1) -- (7,1);
                \draw[line width = 0.4mm] (0,-1) -- (0,1);

                \draw[line width = 0.1mm,dashed] (3.5,1) -- (3.5,-1);

                \draw[thick] plot [smooth,tension=0.9] coordinates{(3.3,1) (3.7,0.5) (3.5,0) (3.3,-0.5) (3.7,-1)};

                \draw[line width = 0.2mm,red] (3.3,1) -- (3.7,-1);

            \end{tikzpicture}
                \caption{S-shape deformation of the cross-section of the two-dimensional beam.}\label{fig:s}
            \end{figure}
        \end{frame}

        \begin{frame}{Validity of the Timoshenko beam - Results from article}
            \centering
            \footnotesize
            \renewcommand{\arraystretch}{0.9}
            Results from \cite{LVV09} and results obtained. $0^a$ indicates a 0 due to rounding. Height to lenght ratio of 1 to 10.

@@

        \begin{frame}{Validity of the Timoshenko beam - Results for different beam shapes}
            \centering
            \footnotesize
            \renewcommand{\arraystretch}{0.8}
            \resizebox{\textwidth}{!}{%
            \begin{tabular}{|cccc||cccc||cccc||cccc|}
                \hline
                \multicolumn{16}{|c|}{Comparison of Eigenvalues} \\
                \hline\hline
                \multicolumn{4}{|c||}{ $h = 1/5$ or $\alpha = 300$} & \multicolumn{4}{c||}{$h =1/10$ or $\alpha = 1200$} & \multicolumn{4}{c||}{$h = 1/20$ or $\alpha = 4800$} & \multicolumn{4}{c|}{$h = 1/30$ or $\alpha = 10800$} \\
                \hline

                {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} & {i} & {2D} & {j} & {Timo} \\
                \hline
                {1}&0.12151&1&0.12092&1&0.031713&1&0.031639&1&0.008013&1&0.008004&1&0.003568&1&0.003565\\
                {2}&3.5460&2&3.5071&2&1.1413&2     & 1.1365 & 2     & 0.30756 & 2     & 0.30705 & 2     & 0.13869 & 2     & 0.13855 \\
                {3} & {7.7311} &       & {-} & {3}     & {7.7161} &       & {-} & 3     & 2.3273 & 3     & 2.3213 & 3     & 1.0698 & 3     & 1.0683 \\
                {4} & 20.225 & 3     & 19.869 & 4     & 7.9180 & 3     & 7.8617 & {4}     & {7.7077} &       & {-} & 4     & 4.0140 & 4     & 4.0058 \\
                {5} & 56.109 & 4     & 54.766 & 5     & 26.148 & 4     & 25.869 & 5     & 8.5086 & 4     & 8.4762 & {5}     & {7.7047} &       & {-} \\
                {6} & {69.164} &       & {-} & 6     & 60.816 & 5     & 59.946 & 6     & 21.911 & 5     & 21.794 & 6     & 10.655 & 5     & 10.625 \\
                {7} & 114.03 & 5     & 110.75 & {7}     & {69.344} &       & {-} & 7     & 45.711 & 6     & 45.390 & 7     & 22.975 & 6     & 22.890 \\
                {8} & {189.17} &  6     & {186.50} & 8     & 115.28 & 6     & 113.23 & {8}     & {69.344} &       & {-} & 8     & 43.113 & 7     & 42.909 \\
                {9} & {192.61} &      &  & {9}     & {191.57} &   7  & {187.55} & 9     & 82.887 & 7     & 82.154 & {9}     & {69.331} &       & {-} \\
                {10} & 285.85 & 7     & 277.64 & {10}    & {192.03} &      & {-} & 10    & 136.03 & 8     & 134.58 & 10    & 73.230 & 8     & 72.803 \\
                {11} & 328.40 & 8     & 330.29 & 11    & 290.76 & 8     & 283.81 & {11}    & {192.48} &       & {-} & 11    & 115.41 & 9     & 114.61 \\
                {12} & {357.08} &       & {-} & {12}    & {374.45} &       & {-} & 12    & 207.29 & 9     & 204.69 & 12    & 171.61 & 10    & 170.20 \\
                {13} & 397.33 & 9     & 394.02 & 13    & 413.20 & 9     & 402.27 & 13    & 298.38 & 10    & 294.10 & {13}    & {192.52} &       & {-} \\
                {14} & 442.00   & 10    & 439.52 & 14    & 558.67 & 10    & 542.65 & {14}    & {376.83} &       & {-} & 14    & 243.56 & 11    & 241.26 \\
                {15} & {533.71} &       & {-} & {15}    & {614.11} &       & {-} & 15    & 410.63 & 11    & 404.01 & 15    & 332.83 & 12    & 329.28 \\
                {16} & 538.97 & 11    & 541.55 & 16    & 726.26 & 11    & 704.15 & 16    & 545.03 & 12    & 535.32 & {16}    & {377.16} &       & {-} \\
                {17} & {596.06} &       & {-} & {17}    & {906.28} &       & {-} & {17}    & {621.95} &       & {-} & 17    & 440.77 & 13    & 435.51 \\
                {18} & 602.77 & 12    & 596.09 & 18    & 913.69 & 12    & 884.92 & 18    & 702.30 & 13    & 688.64 & 18    & 568.51 & 14    & 561.04 \\
                {19} & {657.87} &       & {-} & 19    & 1113.7 & 13    & 1080.1 & 19    & 882.95 & 14    & 864.40 & {19}    & {623.05} &       & {-} \\
                {20} & 717.37 & 13    & 731.74 & {20}    & {1218.0}  &       & {-} & {20}    & {927.18} &       & {-} & 20    & 717.04 & 15    & 706.74 \\
                \hline
                \multicolumn{2}{|c}{Max RE:} & \multicolumn{2}{c||}{3.1718\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{3.1486\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c||}{2.1018\%} & \multicolumn{2}{c}{Max RE:} & \multicolumn{2}{c|}{1.4361\%} \\
                \hline
            \end{tabular}}

            \only<2->{
                \textbf{Conclusion for the Timoshenko beam model:}
                \begin{itemize}
                    \item The Timoshenko beam model compares well with the two-dimensional beam model.
                    \item The shape of the beam influences how well the Timoshenko beam model compares to the two-dimensional beam model.
                    \item The results of the article are confirmed.
                    \item The case of a height to length ration of 1 to 20 is the best case we have tested.
                \end{itemize}
            }

    \subsection{Validity of the Two-dimensional beam model}
        \begin{frame}{Validity of the Two-dimensional beam model}
            \begin{center}
                \begin{minipage}[b]{0.45\linewidth}
                    \centering
                    \begin{tikzpicture}[scale=0.6]
                        \draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
                        \draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
                        \draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
                        \draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);

@@

        \begin{frame}{}

        \begin{frame}
            \begin{table}[htbp]
                \scalebox{.8}{
                \makebox[\textwidth]{
                    \begin{tabular}{|cc|cc|cc|cc||cc|}
                        \hline
                        \multicolumn{10}{|c|}{Comparsion of Eigenvalues with $h = 1/5$, with decreasing $b$ and $b < h$.} \\
                        \hline
                        \hline
                        i     & {b = h} & i     & {b = 1/2 h} & i     & {b = 1/4 h} & i     & {b = 1/8 h} & j     & 2D \\
                        \hline
                        {2} & 0.12307 & {2} & 0.12234 & {2} & 0.12198 & {3} & 0.12178 & 1     & 0.12151 \\
                        {3} & 3.5773 & {5} & 3.5630 & {6} & 3.5558 & {8} & 3.5519 & 2     & 3.5460 \\
                        \rowcolor{lightgray}{5} & 7.7799 & {6} & 7.7596 & {8} & 7.7471 & {11} & 7.7401 & 3     & 7.7311 \\
                        {8} & 20.334 & {9} & 20.283 & {11} & 20.26 & {14} & 20.247 & 4     & 20.225 \\
                        {10} & 56.247 & {12} & 56.173 & {15} & 56.156 & {22} & 56.142 & 5     & 56.109 \\
                        \rowcolor{lightgray}{11} & 69.197 & {14} & 69.319 & {17} & 69.281 & {24} & 69.238 & 6     & 69.164 \\
                        {14} & 114.03 & {16} & 114.01 & {20} & 114.05 & {29} & 114.06 & 7     & 114.03 \\
                        \rowcolor{lightgray}{17} & 187.01 & {19} & 189.14 & {25} & 189.37 & {36} & 189.34 & 8     & 189.17 \\
                        {18} & 192.21 & {20} & 192.41 & {26} & 192.58 & {37} & 192.63 & 9     & 192.61 \\
                        {21} & 284.76 & {23} & 285.43 & {31} & 285.74 & {42} & 285.84 & 10    & 285.85 \\
                        {23} & 327.57 & {26} & 328.24 & {35} & 328.37 & {46} & 328.40 & 11    & 328.40 \\
                        \rowcolor{lightgray}{25} & 347.77 & {28} & 356.44 & {36} & 357.30 & {50} & 357.33 & 12    & 357.08 \\
                        {27} & 393.69 & {30} & 396.84 & {38} & 397.28 & {53} & 397.37 & 13    & 397.33 \\
                        {30} & 434.46 & {34} & 441.05 & {41} & 441.81 & {57} & 441.99 & 14    & 442.00 \\
                        \rowcolor{lightgray}{31} & 523.65 & {36} & 534.04 & {43} & 534.17 & {63} & 534.03 & 15    & 533.71 \\
                        {34} & 550.51 & {37} & 537.82 & {44} & 538.86 & {64} & 539.06 & 16    & 538.97 \\
                        \rowcolor{lightgray}{37} & 590.86 & {41} & 587.43 & {48} & 594.17 & {65} & 595.58 & 17    & 596.06 \\
                        {39} & 590.86 & {42} & 600.52 & {49} & 602.25 & {67} & 602.69 & 18    & 602.77 \\
                        \rowcolor{lightgray}{42} & 646.21 & {44} & 657.22 & {50} & 658.04 & {71} & 658.06 & 19    & 657.87 \\
                        {44} & 711.07 & {46} & 714.62 & {53} & 717.10 & {73} & 717.51 & 20    & 717.37 \\
                        \hline
                        \hline
                        \multicolumn{2}{|c|}{Max RE: \  2.6069\%} &\multicolumn{2}{c|}{Max RE: \ 1.4469\%}  & \multicolumn{2}{c|}{Max RE: \  0.38192\%}  & \multicolumn{2}{c||}{Max RE: \ 0.22301\%}& \multicolumn{2}{c|}{-} \\
                        \hline
                    \end{tabular}%
                    \label{tab:2v3_1}%
                }}
            \end{table}%
        \end{frame}

@@

\section{Conclusion}
    \begin{frame}{Conclusion}
        \begin{itemize}
            \item 
        \end{itemize}

        \textbf{Future Work:}
        \begin{itemize}
            \item Include damping in the models.
        \end{itemize}
